The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-06-15 manuscript.Rmd
edit manuscript...

<!-- We show that the effort is consistent across the better-studied taxa, with ` average_prop_species_seq`% of the fauna sequenced. Using a DNA barcode dataset of ` n_larvae` planktonic larvae, representing ` n_esus` species, collected in coastal waters of Florida, we find a similar proportion of species that can be assigned to a previously sequenced species ( ` format_output(100 * prop_plankton_with_match)`%).  Our results show that most marine species remain to be sequenced. Achieving this goal will required a concerted effort, and resources. -->

<!--
the content of insect traps, marine sediments, plankton
samples, or communities settling on artificial substratum. When applied to
metazoan communities, these sequencing approaches typically target the barcoding
gene and therefore has been dubbed "meta-barcoding". These applications are also
making the public databases for these DNA barcodes all the more valuable. To
deliver on the meta-barcoding promises, it is crucial to have comprehensive
taxonomic coverage represented in the DNA sequences public databases. Here, we
investigate the proportion of species for each marine phylum that have been
sequenced at various spatial scale.
-->

<!-- studies that have summary statistics on what has been sequenced for various marine phyla:
- for Antarctica: Grant+Linse2009-Polar Biology:

We know that some perturbations have large effects because they are visible, but what about perturbations for which we don't see the effects directly because they affect small species? :: checkout nature paper on sea grasses.

- Describing new species is crucial but not sufficient. Without knowing their ranges, and their habitats, we can't study or predict how perturbations of the environment are going to affect their distributions and their susceptibility to perturbations. The process of figuring out the ranges of species is more time consuming than possibly finding new species; and it requires shared knowledge in the community about these new species. Using barcoding and other moleuclar techniques to improve the documentation of species distributions is going to be critical.

@@

Furtheremore, there are important discrepancies in our level of knowledge across phyla. While larger, and accessible groups represent the bulk of the records for marine invertebrates in museum collections, the small organisms, including representatives of the meiofauna are virtually absent. Of the `r n_idigbio_phyla` phyla occurring in iDigBio, `r records_rare_phyla$n_rare_phyla` are represented by less than 500 records, and make up `r records_rare_phyla$prop_rare_phyla`% of the total number of records.

@@

The proportion of species that have DNA barcodes available is relatively constant across the better studied phyla at the scale of the EEZ. It varies between 12% for bryozoans to 28% for cnidarians. The proportions for species known to occur in the Gulf of Mexico are usually similar than for the US, while typically a higher fraction of species from the Pacific Northwest are available. In 2010, it was estimated that a global scale, less than 10% of the species for each marine phylum had been sequenced [@Radulovici2010], suggesting that the US fauna is generally better characterized than the rest of the world, combined with many other species have been sequenced since this report.

@@

This study highlights that we have too little data about too few species of marine invertebrates, we recommend that additional coordinated field expeditions are organized to sample more thoroughly the marine environment. Data from museum collections make clear that any additional samples will contain new species and new records. Samples collected during these expeditions need to be photographed to document live appearance that would otherwise be lost during preservation. We also need to capture metadata associated with the specimens to be able to understand better the physical characteristics of the habitats for these species. Specimens need to be sub-sampled and have tissues suitable for genomic analysis preserved for their DNA barcode, or any other genomic resources. Some of these parts of data and specimen collection can be automated and captured digitally directly in the field speeding up data collection.

@@

<!-- Beyond their utility in documenting diversity, metabarcoding is also promising for understanding the functioning of ecosystems. -->

>>>>

@@

Furthermore, there are important discrepancies in our level of knowledge across phyla. While larger, and accessible groups represent the bulk of the records for marine invertebrates in museum collections, the small organisms, including representatives of the meiofauna are virtually absent. Of the `r n_idigbio_phyla` phyla occurring in iDigBio, `r records_rare_phyla$n_rare_phyla` are represented by less than 500 records, and make up `r records_rare_phyla$prop_rare_phyla`% of the total number of records.

@@

The proportion of species that have DNA barcodes available is relatively constant across the better studied phyla at the scale of the EEZ. It varies between 12% for bryozoans to 28% for cnidarians. The proportions for species known to occur in the Gulf of Mexico are usually similar than for the US, while typically a higher fraction of species from the Pacific Northwest are available. In 2010, it was estimated that a global scale, less than 10% of the species for each marine phylum had been sequenced [@Radulovici2010], and that this number was even lower in some areas (e.g. 2.6% for the Antarctic [@Grant2009]). This suggests that even as many additional species have had their DNA barcodes made available since these studies, the US fauna is generally better characterized than other parts of the world.

@@

This study highlights that we have too little data about too few species of marine invertebrates, we recommend that additional coordinated field expeditions are organized to sample more thoroughly the marine environment. The relation between sampling effort and diversity from museum collections makes clear that any additional samples will improve greatly our knowledge of marine biodiversity.

Samples collected during these expeditions need to be photographed to document live appearance that would otherwise be lost during preservation. We also need to capture metadata associated with the specimens to be able to understand better the physical characteristics of the habitats for these species. Specimens need to be sub-sampled to create material suitable for genomic analysis. Parts of data and specimen collection can be automated and captured digitally directly in the field speeding up data collection.

@@

In order to predict the impact of climate change and other anthropogenic perturbations on species distributions, we need to collect more occurences for species. One potential challenge for this is to be able to convey taxonomic concepts for mostly unamed species. Developing robust identifiers that can be used across biodiversity information systems, and potentially anchored in results from DNA barcoding or other molecular techniques, is needed to collaboratively build our knowledge of species distributions.

Beyond their utility in documenting diversity, metabarcoding is also a promising technology to monitor changes in communities and for understanding the functioning of ecosystems. For instance, despite our limited knowledge of the diversity of communities in the meiofauna, metabarcoding could be used to detect and documents changes in species assemblages following the Deepwater Horizon Oil Spill [@Bik2012]. Metabarcoding has also been used to reveal important differences in the diet of 3 related species of fishes that co-occur [@Leray2015b], providing a much more detailed understanding of trophic relations.
